|

### 2016-06-28 SAMPLES/FTP/Manual-FTP.Rmd
manuals
manual

![docker pull](../../media/docker-pull.png)
```
eval $(docker-machine env default)
docker pull kristiyanto/p3
docker run --rm -v ~/Desktop/PXD001468:/root/data kristiyanto/p3
```

![docker run](../../media/docker-run.png)

@@

If the process stop returning error:
* Make sure all the required files are in the folder. E.g: Fasta files sometimes are not provided in the FTP/Pride repository and must be provided manually. 
* Remove all \*.tmp files before re-run the containers.

>>>>

![docker pull](../../media/docker-pull.png)
```
eval $(docker-machine env default)
docker pull kristiyanto/p3

# Mac/Linux
docker run --rm -v ~/Desktop/PXD001468:/root/data kristiyanto/p3

## On Windows:
docker run --rm -v /c/Users/daniel/Desktop/PXD001468:/root/data kristiyanto/p3
```

![docker run](../../media/docker-run-ftp.png)

@@

If the process stop returning error:
* Make sure all the required files are in the folder. E.g: In the case fasta file is not provided in the FTP/Pride repository and must be provided manually. 
* Remove all \*.tmp files before re-run the containers.

### 2016-06-28 SAMPLES/PrideID/Manual-PrideID.Rmd
manuals
manual

![docker pull](../../media/docker-pull.png)
```
eval $(docker-machine env default)
docker pull kristiyanto/p3
docker run --rm -v ~/Desktop:/root/data kristiyanto/p3
```

>>>>

![docker pull](../../media/docker-pull.png)
```
eval $(docker-machine env default)
docker pull kristiyanto/p3

# Mac/Linux
docker run --rm -v ~/Desktop/PXD001468:/root/data kristiyanto/p3

## On Windows:
docker run --rm -v /c/Users/daniel/Desktop/PXD001468:/root/data kristiyanto/p3
```
